%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {M.Sc. in Computer Science (Grid Computing), Grade 8.0} % Degree
    {University of Amsterdam} % Institution
    {Amsterdam, The Netherlands} % Location
    {2010 -- 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Master's specializing in Grid Computing, UvA's program in large-scale distributed systems and parallel computation.}
        \item {Funded in full for the 24-month duration by a merit-based Huygens Scholarship Programme award (Dutch government, via Nuffic).}
        \item {Thesis: ``Method for Tracking and Tracing Idea Reuse,'' covering algorithms for detecting content reuse and attributing credit across collaborative platforms; conducted in collaboration with Beonten Inc. (Boston) and partially backed by the US National Science Foundation.}
        \item {External supervisor: Prof. Marshall Van Alstyne (Boston University, coauthor of \emph{Platform Revolution}); the work resulted in a co-invented US patent filing.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {B.Sc. in Computer Software Engineering} % Degree
    {Amirkabir University of Technology} % Institution
    {Tehran, Iran} % Location
    {2004 -- 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Bachelor's in Computer Software Engineering (5-year program) at Amirkabir University of Technology, one of Iran's most respected technical universities.}
        \item {Member of the only Amirkabir team from my year to qualify for the ACM-ICPC Asia West Regional Programming Contest, the regional stage of the world's most established competitive-programming competition.}
        \item {During the degree, co-built the university's full virtual education software stack from the ground up with a classmate, eventually serving thousands of students attending live online classrooms remotely.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
