%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Co-Founder \& CTO} % Job title
    {\href{https://www.xecolabs.com}{Xeco Labs}} % Organization
    {Amsterdam, The Netherlands} % Location
    {Nov. 2017 -- Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Co-founded Xeco Labs and built it into the senior-led technical partner of record for asset managers and fund administrators; currently wrapping a successful five-year engagement with AssetCare and opening capacity for new fintech and AI-native partnerships.}
        \item {Technical partner to IndexPeople (asset manager, since 2018) and AssetCare (fund administrator, 2021 to 2026); mentored AssetCare's incoming in-house engineering team through a clean handover to internal ownership.}
        \item {Architected Fundtech end to end, AssetCare's proprietary fund-administration platform now running live operations for institutional clients including VanEck (digital-asset ETNs), Atradius, and Stichting Pensioenfonds Flexsecurity, across liquid, illiquid, and hybrid fund strategies.}
        \item {Built the platform's data backbone supporting 80+ fund managers across \textasciitilde120 funds, with 13,000+ transactions and 75,000+ investor reports processed to date, plus automated ingestion from banks, brokers, exchanges, and on-chain protocols.}
        \item {Translated dense EU financial regulation (AIFMD, MiFID 2, DORA, GDPR) into modular, test-covered services, enabling major features to ship on a 2 to 3 week cadence on mature production systems.}
        \item {Delivered 99.99\% uptime across all services shipped, via disciplined release practices, observability baselines, and incident reviews run jointly with client operations teams.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Founder \& Photographer} % Job title
    {Drifting Horizon} % Organization
    {Amsterdam, The Netherlands} % Location
    {Apr. 2023 -- Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {A photography practice focused on people, place, and quiet moments; editorial, lifestyle, and street work for clients in Amsterdam and beyond.}
        \item {Launched with TUI (European travel group) as the founding commercial client, anchoring the practice in editorial-grade work from day one.}
        \item {Run the business end to end: positioning, client relationships, shoots, post-production, and delivery.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer (Freelance)} % Job title
    {Navan} % Organization
    {Amsterdam, The Netherlands} % Location
    {Apr. 2021 -- Jul. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Joined Navan (then TripActions) on a 4-month senior freelance engagement to bring global rail into the platform's inventory, working alongside an 8 to 10 person engineering team.}
        \item {Integrated a global train inventory spanning SNCF, Deutsche Bahn, Trenitalia, Eurostar, Amtrak, and Trainline.com, making rail a first-class booking option alongside flights and hotels.}
        \item {Designed and built a unified train ticketing API that normalized each provider's quirks (including legacy SOAP services) into a single clean interface for the rest of the platform to consume.}
        \item {Closed the engagement with a Staff Software Engineer offer from Navan to convert to full-time.}
        \item {Tech: Java, Microservices, SOAP, Maven.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-Founder \& CTO} % Job title
    {SPEQT} % Organization
    {Amsterdam, The Netherlands} % Location
    {Jan. 2020 -- Mar. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Bootstrapped B2B fintech offering disposable business bank accounts paired with an expense management layer for SMEs; co-founded with two others, owning technology end to end while they led product and execution.}
        \item {Architected and shipped the full SPEQT stack from scratch on top of Treezor (French Banking-as-a-Service), where SPEQT became Treezor's first Netherlands-based client.}
        \item {Built the platform around the three pieces of NL infrastructure the product depended on: business IBANs (the core unit our customers issued and operated against), Maestro cards (the dominant local debit rail required for the expense card layer), and iDEAL (the leading domestic scheme businesses use to fund accounts).}
        \item {Bootstrapped the venture entirely through Xeco Labs with no outside capital, keeping the founding team in full control of pace and decisions.}
        \item {Made the disciplined call with co-founders to wind operations down once Treezor could not deliver those NL rails on a workable timeline, rather than burn runway against a stuck dependency.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer (Freelance)} % Job title
    {\href{https://travelbird.nl/}{TravelBird}} % Organization
    {Amsterdam, The Netherlands} % Location
    {Apr. 2017 -- Jun. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Returned to TravelBird on a focused 3-month senior freelance engagement to ship core inventory integrations across the backend, data, and search stack.}
        \item {Led design and implementation of core integrations with Amadeus and Eurotours channel managers, automating ingestion of hotel inventory, availability, and pricing across tens of thousands of properties.}
        \item {Replaced manual booking workflows with robust, search-driven pipelines, freeing the operations team from one-by-one entry and expanding the live inventory available to customers.}
        \item {Wrapped legacy SOAP provider APIs in clean abstractions, partnering closely with product and operations to land the engagement end to end.}
        \item {Tech: Python, Django, MySQL, Elasticsearch.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Mobile Engineering Lead (Freelance)} % Job title
    {Eneco} % Organization
    {Amsterdam, The Netherlands} % Location
    {Sep. 2016 -- Feb. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Brought in by Quby, maker of the Toon smart thermostat (one of the Netherlands' most established connected-home products) and then mid-merger into parent Eneco, as senior freelance lead to oversee the mobile app roadmap and prepare the path to bring mobile development in-house from the existing offshore team.}
        \item {Defined the mobile roadmap and architectural vision for Toon's next generation of consumer iOS and Android apps, working directly with Quby product and Eneco senior leadership.}
        \item {Owned technical direction and quality-gate responsibility for the offshore development team (2 iOS, 2 Android), raising delivery consistency and code quality across the cross-platform mobile stack.}
        \item {Designed and ran the internal mobile hiring program, leading screening and technical interviews for the planned in-house team.}
        \item {Wrapped the engagement when a wider Eneco-Quby reorganization paused the in-house transition, having stabilized the roadmap and the offshore team for the merged organization to carry forward.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-Founder \& Technical Lead} % Job title
    {FIND A SHELF} % Organization
    {The Randstad, The Netherlands} % Location
    {Sep. 2015 -- Dec. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Co-founded a retail-tech venture: started as ``Airbnb for shelf space'' in physical stores, pivoted to a curated European wholesale marketplace in the shape of Etsy Wholesale, and wound the business down once unit economics didn't justify the operational lift.}
        \item {Designed and built the core platform end to end in Python, Django, and PostgreSQL, owning architecture, MVP delivery, and the iteration loop through both versions of the product.}
        \item {Ran in-person market validation across major Dutch cities, walking into physical retailers to pressure-test demand directly with shop owners, producing the data that drove the eventual pivot.}
        \item {Co-led the pivot to curated European wholesale and shipped enough of the new product to land unique maker goods on boutique and concept-store shelves across the Netherlands.}
        \item {First paired here with the co-founder I went on to build Xeco Labs with.}
        \item {Tech: Python, Django, PostgreSQL, Ansible, AWS.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Software Engineer} % Job title
    {\href{https://travelbird.nl/}{TravelBird}} % Organization
    {Amsterdam, The Netherlands} % Location
    {Jun. 2015 -- Mar. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Joined TravelBird as the lead engineer of the team tasked with automating internal operations; the company had launched as a human-intensive travel-deals business with staff manually bundling packages for travelers across the EU.}
        \item {Led the team that automated TravelBird's back-office stack end to end, replacing manual refund processing, inventory expansion, and supplier-booking workflows with software the operations team could trust.}
        \item {Built the integrations layer that let TravelBird scale its supplier and inventory footprint without scaling operations headcount in lockstep, a key enabler of the company's EU growth phase.}
        \item {Worked directly with operations and product to sequence the automation roadmap by business impact, shipping the highest-leverage tooling first.}
        \item {Contributed to engineering team growth through screening, technical interviews, and hire evaluation.}
        \item {Tech: Python, Django, Elasticsearch, MySQL, Automation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Mobile Development Team Lead} % Job title
    {\href{https://www.tmg.nl/nl}{TMG}} % Organization
    {Amsterdam, The Netherlands} % Location
    {Mar. 2014 -- May. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Promoted into mobile team lead following the full integration of Hyves into TMG (Telegraaf Media Groep, the largest Dutch media group, publisher of De Telegraaf and other national titles).}
        \item {Led the mobile team responsible end to end for full-stack mobile delivery across all TMG news titles (flagships including Telegraaf and Telesport), spanning mobile websites, native iOS and Android apps, and the supporting backend services.}
        \item {Shipped two native iOS and Android apps for the 2014 FIFA World Cup where Dutch football fans predicted match outcomes and earned points across the tournament, reaching millions of active users; delivered on time and without a production incident through the entire tournament window.}
        \item {Owned technical direction across mobile and backend, raising delivery quality, reliability, and maintainability in production.}
        \item {Onboarded new mobile hires and served on TMG's tech department hiring squad, running weekly technical interviews across mobile, backend, and full-stack roles.}
        \item {Tech: iOS, Android, Python, Flask, Django.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Developer} % Job title
    {\href{https://www.tmg.nl/nl}{TMG}} % Organization
    {Amsterdam, The Netherlands} % Location
    {Dec. 2013 -- Feb. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Joined TMG as a senior mobile engineer immediately following the integration of Hyves into the group, contributing native mobile and backend work before being promoted into team lead.}
        \item {Built and shipped native mobile features for iOS and Android, and contributed to the backend systems supporting them.}
        \item {Worked closely with product and design to ship user-facing improvements with strong quality standards.}
        \item {Tech: iOS, Android, Python, Flask, Django.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Hyves} % Organization
    {Amsterdam, The Netherlands} % Location
    {Oct. 2012 -- Dec. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {First role in the Netherlands, joining Hyves (the country's dominant social network at the time, \textasciitilde10M monthly active users in a country of 17M, and the only meaningful local competitor to Facebook) directly out of university after passing an extensive, technically deep hiring loop.}
        \item {By the time I joined, Hyves had been acquired by TMG, with several teams building mobile experiences for TMG-owned titles alongside the core social network.}
        \item {Spent the probation period working on the core Hyves platform in PHP, fixing production issues at consumer scale and shipping changes through an elaborate release process targeting hundreds of production servers.}
        \item {Moved into the mobile team as a full-stack engineer post-probation, choosing mobile as the specialty I would carry through subsequent roles.}
        \item {Built and shipped mobile experiences for TMG-owned titles including De Telegraaf and DFT (the financial daily) using the team's hybrid architecture, partnering with backend engineers and product on stability, performance, and user experience at high traffic.}
        \item {Tech: PHP, Python, MySQL, iOS, Android.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer (Part-time, Remote)} % Job title
    {Beonten, Inc.} % Organization
    {Boston, MA} % Location
    {Sep. 2011 -- Mar. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Early contributor to a Boston-based platform startup focused on attributing users for their knowledge contributions, working directly with a small team led by Marshall Van Alstyne (Boston University; coauthor of the international bestseller \emph{Platform Revolution} and a leading authority on network business models) on research backed in part by the US National Science Foundation.}
        \item {The collaboration became the subject of my MSc thesis at the University of Amsterdam, with Van Alstyne serving as external supervisor.}
        \item {Designed and built the document reuse detection and attribution module that identified repeated text fragments across submissions and produced a reuse graph and tree visualization of the relationships.}
        \item {Co-inventor with Van Alstyne on a US patent (``Method for Tracking and Tracing Idea Reuse'') on algorithms developed during the engagement; the application lapsed without commercialization.}
        \item {Worked closely with the team to translate research-heavy requirements into a working production feature, balancing academic rigor against practical delivery on a small startup team.}
        \item {Tech: Python, Django.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Software Engineer (Part-time)} % Job title
    {Tehran Polytechnic Virtual Education Center} % Organization
    {Tehran, Iran} % Location
    {Apr. 2008 -- Aug. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {As students at Tehran Polytechnic, a classmate and I built the university's entire virtual education software stack from the ground up, eventually serving thousands of students attending live online classrooms remotely.}
        \item {Designed and implemented the core architecture of the university's learning management system end to end.}
        \item {Built the infrastructure for simultaneous live multimedia virtual classrooms, supporting thousands of remote students concurrently.}
        \item {Owned delivery across backend, real-time classroom features, and operational stability in production.}
        \item {Tech: Java, JBoss, Flex/ActionScript, Oracle DB.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {DPCO} % Organization
    {Tehran, Iran} % Location
    {Mar. 2006 -- Dec. 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed to a nationwide telecom network management initiative, building systems for operational monitoring and management of telecommunications infrastructure.}
        \item {Worked on the ISMN (Iran Switch Management Network) project as part of the technical design and implementation team.}
        \item {Developed backend components for network operations and traffic management, focusing on reliability and maintainability in a mission-critical environment.}
        \item {Collaborated with cross-functional stakeholders to translate operational requirements into production-ready software.}
        \item {Tech: Java, Microservices, Oracle Database.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
