%-------------------------------------------------------------------------------
\cvsection{Selected Experience}
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Co-Founder \& CTO} % Job title
    {\href{https://www.xecolabs.com}{Xeco Labs}} % Organization
    {Amsterdam, The Netherlands} % Location
    {Nov. 2017 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Co-founded the senior-led technical partner of record for asset managers and fund administrators; technical partner to IndexPeople (since 2018) and AssetCare (2021 to 2026); now opening capacity for new fintech and AI-native partnerships.}
        \item {Architected Fundtech end to end, AssetCare's fund-administration platform running live for VanEck (digital-asset ETNs), Atradius, and Pensioenfonds Flexsecurity; 99.99\% uptime, 80+ fund managers, 13,000+ transactions, 75,000+ investor reports.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer (Freelance)} % Job title
    {Navan} % Organization
    {Amsterdam, The Netherlands} % Location
    {Apr. 2021 -- Jul. 2021} % Date(s)
    {
      \begin{cvitems}
        \item {Brought global rail (SNCF, Deutsche Bahn, Eurostar, Trainline) into the platform via a unified ticketing API normalizing legacy SOAP providers; closed with a Staff Software Engineer offer.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-Founder \& CTO} % Job title
    {SPEQT} % Organization
    {Amsterdam, The Netherlands} % Location
    {Jan. 2020 -- Mar. 2021} % Date(s)
    {
      \begin{cvitems}
        \item {Co-founded a B2B fintech (disposable business bank accounts paired with an expense management layer); built the full stack on Treezor BaaS, becoming their first NL-based client across IBAN, Maestro, and iDEAL rails.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-Founder \& Technical Lead} % Job title
    {FIND A SHELF} % Organization
    {The Netherlands} % Location
    {Sep. 2015 -- Dec. 2016} % Date(s)
    {
      \begin{cvitems}
        \item {Co-founded a retail-tech venture; built the platform end to end (Python, Django, AWS), pivoted from ``Airbnb for shelf space'' to curated European wholesale, and wound down on a disciplined unit-economics call.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Software Engineer} % Job title
    {\href{https://travelbird.nl/}{TravelBird}} % Organization
    {Amsterdam, The Netherlands} % Location
    {Jun. 2015 -- Mar. 2016} % Date(s)
    {
      \begin{cvitems}
        \item {Led the team that automated TravelBird's back-office stack end to end, replacing manual refund, inventory, and supplier-booking workflows; a key enabler of the company's EU growth phase.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Mobile Development Team Lead} % Job title
    {\href{https://www.tmg.nl/nl}{TMG}} % Organization
    {Amsterdam, The Netherlands} % Location
    {Mar. 2014 -- May. 2015} % Date(s)
    {
      \begin{cvitems}
        \item {Led mobile delivery across TMG news titles (Telegraaf, Telesport); shipped two native iOS/Android apps for the 2014 FIFA World Cup that reached millions of users and ran the entire tournament without a production incident.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Hyves} % Organization
    {Amsterdam, The Netherlands} % Location
    {Oct. 2012 -- Dec. 2013} % Date(s)
    {
      \begin{cvitems}
        \item {Joined the country's dominant social network (\textasciitilde10M MAU, post-TMG acquisition) directly out of university; shipped on the core PHP platform and the mobile team building experiences for De Telegraaf and DFT.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
